Dynein project log

### 2016-09-19 thesis_stuff/thesis_stuff.tex
Add right equilibrium angle figures and cool crystal structures to thesis_stuff.tex.

\begin{figure}[h!]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../figures/Post_powerstroke_tomography.jpg}
    \caption{Post-powerstroke equilibrium angles from EM tomography.}
  \end{minipage}
  \hspace{5mm}
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../figures/Pre_powerstroke_tomography.jpg}
    \caption{Pre-powerstroke equilibrium angles from EM tomography.}
  \end{minipage}
  \label{fig:em_tomography_eq_angles}
\end{figure}

>>>>

\begin{figure}[h!]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../figures/Post_powerstroke_tomograph.jpg}
    \caption{Post-powerstroke equilibrium angles from EM tomography.}
  \end{minipage}
  \hspace{5mm}
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../figures/Pre_powerstroke_tomograph.jpg}
    \caption{Pre-powerstroke equilibrium angles from EM tomography.}
  \end{minipage}
  \label{fig:em_tomography_eq_angles}
\end{figure}
